InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

tmp.df4 <- tmp.df4%>%
  group_by(ssid, tNo, trialUnq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
  mutate(hr_loss_prop = 1 - hr_valid_prop)

@@

colnames(tmp.df4)
write_csv(tmp.df4, 'interodata_clean_gp.csv')

>>>>

tmp.df4 <- tmp.df4 %>%
  group_by(ssid, tNo, trialUnq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
  mutate(hr_loss_prop = 1 - hr_valid_prop)

@@

colnames(tmp.df4)
write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')
